ASR-Output-Correcting Webapp After 6 Years

### 2018-03-23 2018-tsd-brno/webapp.tex
motivation

@@

>>>>

\subsection{Motivation}

Our project focuses on the collection of recordings of Karel Mako\v{n} *1912
\textdagger1993, the author of numerous books, translations and comments to
works of spiritual and religious nature, who was influenced by trances during
recurring surgery without anesthesy in the age of 6, ecstasies in the youth and
finally facing and surviving certain death in a Nazi concentration camp, after
which he experienced enlightenment. He gave talks in a narrow circle of friends
and the recordings in our care have been taken between early 70's and 1991,
spanning about 1000 hours in total.

All of his work deals more or less directly with a single topic: entering the
eternal life before the physical death. He draws mainly from the Christian
symbolism, builds up on Christian mysticism and ancient tradition of India.

Basically the meat of his teachings is systematically encompassed in his written
works, whereas the talks contain the sauce: talks tailored to the audience,
answering questions, personal experiences, behind-the-scenes to the books etc.

@@

One major difference to a wiki is that wiki is creative, whereas our task is
mechanical. The user has basically no room for their own invention: providing a
different than correct transcription is seen as an error.

Major wikis have good measures for edit conflicts, which is where we could learn
some lessons. However, so far there was no need to do that because
\begin{enumerate}
\item{when we always simply take the most recent version
of a segment, the result stays consistent even if a piece from user A comes into
a larger transcription of user B;}
\item{our user base is so far limited to a small community who have no problem
coordinating with each other. We plan to expand to broader public soon though.}
\end{enumerate}

% alert when correcting humanic
